### 2022-03-03 paper/paper.tex
branch-and-bound algorithm; not yet integrated into package

% Language selector
\newif\ifen
%\enfalse % Change to false to export Korean

@@

\ifen
We refer to this problem as the \emph{optimal college application portfolio,} as follows: Consider a college market with $m$ colleges. The $j$th college is named $c_j$. Consider a single prospective student in this market, and let each $t_j$-value indicate the utility she associates with attending $c_j$, where her utility is $t_0$ if she does not attend college. Let $g_j$ denote the application fee for $c_j$ and $H$ the student's total budget to spend on application fees. Finally, let $f_j$ denote her probability of being admitted to $c_j$ if she applies, so that $Z_j$ equals one if she is admitted and zero if not. It is appropriate to assume that the $Z_j$ are probabilistically independent as long as $f_j$ are probabilities estimated specifically for this student (as opposed to generic acceptance rates). Then the student's objective is to maximize the expected utility associated with the best school she gets into within this budget. Her optimal college application strategy is given by the solution $\mathcal{X}$ to the problem above, where $\mathcal{X}$ represents the set of schools to which she applies.
\else
다음 해석에 따라 이를 `최적 대학 지원 포트폴리오 문제'라고 부른다. $m$개의 대학교를 가지는 입학 시장을 고려하자. $j$번째 학교의 이름은 $c_j$이다. 이 시장에 참여하는 한 학생을 고려해서 그가 $c_j$에 진학하면 $t_j$ 단위의 효용이 발생한다고 하자. 단, 어떤 대학에도 진학하지 않는 경우 그의 효용은 $t_0$이다. $c_j$의 지원비가 $g_j$이며 학생이 지원비에 쓸 수 있는 예산이 $H$라고 하자. 마지막, $c_j$에 지원하면 학생이 합격할 확률이 $f_j$이라고 하자. 따라서 합격하면 $Z_j = 1$, 합격 안 하면 $Z_j = 0$이 된다. $f_j$가 (학교의 전체적인 합격률이 아니라) 바로 이 학생의 합격 확률일 때 $Z_j$의 확률적 독립성을 적절한 가정이다. 그러면 학생의 목표는 주어진 예산 안에서 학생이 합격하는 가장 좋은 학교의 기대 효용을 최대화하는 것이다. 위 문제의 최적해가 $\mathcal{X}$일 때, 학생의 최적 대학 지원 전략은 $\mathcal{X}$에 지원하는 것이다.
\fi

As Chao (2014) remarked, college application represents a somewhat subtle portfolio optimization problem. Traditional portfolio optimization models weigh the expected profit across all assets against a risk term, yielding a concave maximization problem with linear constraints (Meucci 2005). But college applicants maximize the observed value of their \emph{best} asset: If a student is admitted to her $j$th choice, then she is indifferent as to whether she gets into her $(j+1)$th choice. As a result, the valuation function that students maximize is \emph{convex} in the expected utility associated with individual applications. Risk management is implicit in the college application problem because, in a typical admissions market, college preferability is negatively correlated with competitiveness. That is, students  negotiate a tradeoff between highly attractive, selective “reach schools” and less preferable “safety schools” where admission is a safer bet. Finally, the combinatorial nature of the college application problem makes it difficult to solve using the gradient-based techniques used in continuous portfolio optimization. Chao estimated her model (which considers application as a \emph{cost} rather than a constraint) by clustering the schools so that $m=8$, a scale at which enumeration is tractable. Our study pursues a more general solution.

We take special interest in the validity of greedy solution algorithms, such as that that iteratively adds the asset that yields the greatest increase in the objective function until the budget is exhausted. Greedy algorithms produce a \emph{nested} family of solutions, parameterized by the budget $H$: If $H \leq H'$, then the greedy solution for budget $H$ is a subset of the greedy solution for budget $H'$. As Rozanov and Tamir (2020) remark, this nestedness property is useful not only for obtaining an optimal solution, but in the implementation thereof under uncertain information. For example, in the United States, many college applications are due at the beginning of November, and it is typical for students to begin working on their applications during the prior summer because colleges expect students to tailor their essays to the target school. However, students may not know how many schools they can afford to apply to until late October. The nestedness property---or equivalently, the validity of a greedy algorithm---implies that even in the absence of complete budget information, students can begin to carry out the optimal application strategy by writing essays for schools in the order that they enter the maximal portfolio.

@@

\parskip 0em
\leftskip 2em
\parindent -2em
Budish, Eric. 2011. ``The Combinatorial Assignment Problem: Approximate Competitive Equilibrium from Equal Incomes.'' \emph{Journal of Political Economy} 119 (6): 1061--1103. \url{https://doi.org/10.1086/664613}.

@@

>>>>

% Language selector
\newif\ifen
\entrue % Change to false to export Korean

@@

\ifen
We refer to this problem as the \emph{optimal college application portfolio,} as follows: Consider a college market with $m$ colleges. The $j$th college is named $c_j$. Consider a single prospective student in this market, and let each $t_j$-value indicate the utility she associates with attending $c_j$, where her utility is $t_0$ if she does not attend college. Let $g_j$ denote the application fee for $c_j$ and $H$ the student's total budget to spend on application fees. Lastly, let $f_j$ denote her probability of being admitted to $c_j$ if she applies, so that $Z_j$ equals one if she is admitted and zero if not. It is appropriate to assume that the $Z_j$ are probabilistically independent as long as $f_j$ are probabilities estimated specifically for this student (as opposed to generic acceptance rates). Then the student's objective is to maximize the expected utility associated with the best school she gets into within this budget. Her optimal college application strategy is given by the solution $\mathcal{X}$ to the problem above, where $\mathcal{X}$ represents the set of schools to which she applies.
\else
다음 해석에 따라 이를 `최적 대학 지원 포트폴리오 문제'라고 부른다. $m$개의 대학교를 가지는 입학 시장을 고려하자. $j$번째 학교의 이름은 $c_j$이다. 이 시장에 참여하는 한 학생을 고려해서 그가 $c_j$에 진학하면 $t_j$ 단위의 효용이 발생한다고 하자. 단, 어떤 대학에도 진학하지 않는 경우 그의 효용은 $t_0$이다. $c_j$의 지원비가 $g_j$이며 학생이 지원비에 쓸 수 있는 예산이 $H$라고 하자. 마지막, $c_j$에 지원하면 학생이 합격할 확률이 $f_j$이라고 하자. 따라서 합격하면 $Z_j = 1$, 합격 안 하면 $Z_j = 0$이 된다. $f_j$가 (학교의 전체적인 합격률이 아니라) 바로 이 학생의 합격 확률일 때 $Z_j$의 확률적 독립성을 적절한 가정이다. 그러면 학생의 목표는 주어진 예산 안에서 학생이 합격하는 가장 좋은 학교의 기대 효용을 최대화하는 것이다. 위 문제의 최적해가 $\mathcal{X}$일 때, 학생의 최적 대학 지원 전략은 $\mathcal{X}$에 지원하는 것이다.
\fi

\ifen
As Chao (2014) remarked, college application represents a somewhat subtle portfolio optimization problem. In computational finance, traditional portfolio optimization models weigh the expected profit across all assets against a risk term, yielding a concave maximization problem with linear constraints (Meucci 2005). But college applicants maximize the value of their \emph{best} asset: If a student is admitted to her $j$th choice, then she is indifferent as to whether she gets into her $(j+1)$th choice. As a result, the valuation function that students maximize is \emph{convex} in the expected utility associated with individual applications. Risk management is implicit in the college application problem because, in a typical admissions market, college preferability is negatively correlated with competitiveness. That is, students negotiate a tradeoff between highly attractive, selective “reach schools” and less preferable “safety schools” where admission is a safer bet (Kim 2015). Finally, the combinatorial nature of the college application problem makes it difficult to solve using the gradient-based techniques used in continuous portfolio optimization. Chao estimated her model (which considers application as a \emph{cost} rather than a constraint) by clustering the schools so that $m=8$, a scale at which enumeration is tractable. Our study pursues a more general solution.
\else
Chao (2014)가 주장한 바처럼 대학 지원 전략은 약간 미묘한 포트폴리오 최적화 문제이다. 재정학 분야에서 고전적 포트폴리오 최적화 모형은 전체 자산의 총이익에서 위험회피 항을 뺌으로 선형식으로 제약된 오목 최대화 문제를 이룬다 (Meucci 2005). 그러나 대학 지원자는 가치가 제일 높을 단 한 자산의 가치를 최대화하고자 한다. 어떤 학생이 자신의 $j$위 학교에 합격하면, $(j+1)$위 학교에 합격하든 불합격하든 무관심하기 때문이다. 이에 따라 학생이 최대화하려는 함수는 각 지원의 기대 효용에 대해 오목이 아닌 볼록 함수이다. 또한 전형적인 입학 시장에서 대학의 효용과 합격 확률이 서로 반비례하므로 대학 지원 문제에 위험 관리가 내포 되어 있다. 선호도가 높으며 붙기 어려운 “상향학교”(reach school)와 선호도가 낮으며 붙기 쉬운 “안정학교”(safety school) 사이의 균형을 고려해야 하기 때문이다 (김민희 2015). 마지막, 대학 지원의 조합적인 본성 때문에 연속적인 포트폴리오 최적화 문제에서 흔히 사용하는 기울기 방법으로 풀기가 어렵다. Chao는 지원을 제약 조건 대신 비용으로 모형화했으며 모형을 추정하기 위해 $m=8$이 되도록 학교를 먼저 클러스터로 모았다. 이는 열거법을 통해 문제를 쉽게 풀 수 있는 규모이었지만 본 연구는 더 일반적인 해법을 목표로서 추구한다.
\fi

\ifen
We take special interest in the validity of greedy solution algorithms, such as that that iteratively adds the asset that yields the greatest increase in the objective function until the budget is exhausted. Greedy algorithms produce a \emph{nested} family of solutions, parameterized by the budget $H$: If $H \leq H'$, then the greedy solution for budget $H$ is a subset of the greedy solution for budget $H'$. As Rozanov and Tamir (2020) remark, the knowledge that the optima are nested aids not only in computing the optimal solution, but in the implementation thereof under uncertain information. For example, in the United States, many college applications are due at the beginning of November, and it is typical for students to begin working on their applications during the prior summer because colleges expect students to tailor their essays to the target school. However, students may not know how many schools they can afford to apply to until late October. The nestedness property---or equivalently, the validity of a greedy algorithm---implies that even in the absence of complete budget information, students can begin to carry out the optimal application strategy by writing essays for schools in the order that they enter the maximal portfolio.
\else
본 연구에서 특히 탐욕 해법의 타당성에 관심을 기울인다. 예를 들어 예산이 다 소비될 때까지 목적 함수를 가장 빨리 증가시키는 학교를 차례대로 선택하는 알고리즘은 일종의 탐욕 해법이다. 탐욕 해법 예산 $H$으로 모수화된 해의 순서를 유도하며 `포함 사슬 관계` (nestedness) 성질로 연결된다. $H \leq H'$일 때, 예산 $H$에 해당하는 탐욕 해는 예산 $H'$에 해당하는 탐욕 해의 부분집합이다. Rozanov과 Tamir (2020)이 주장하듯, 최적해가 포함 사슬 관계를 가짐을 알면 최적해를 구하는 데일 뿐더러 정보가 불확실한 상황에서 최적해를 이행하는 데에도 유용하다. 가령 많은 미국 대학의 지원 기한은 11월 초인데 지원 에세이를 학교의 취향을 맞춰서 작성해야 하므로 여름부터 원서를 작성하는 학생이 많다. 그러나 시간이나 지원비에 대한 예산을 10월 말까지 모를 수도 있다. 포함 사슬 관계 성질, 또는 탐욕 해법의 타당성은 완전한 예산 정보가 없음에도 학교가 최적 포트폴리오에 진입하는 순서대로 원서를 작성하는 식으로 최적 전략을 이행할 수 있다고 의미한다.
\fi

@@

\parskip 0em
\leftskip 2em
\parindent -2em
\ifen \else
김민희. 2015. ``{[대입 수시 전략]} 총 6번의 기회 \textellipsis `상향·소신·안정' 분산 지원하라.'' 중앙일보, 8월 26일. \url{https://www.joongang.co.kr/article/18524069}.\fi

Budish, Eric. 2011. ``The Combinatorial Assignment Problem: Approximate Competitive Equilibrium from Equal Incomes.'' \emph{Journal of Political Economy} 119 (6): 1061--1103. \url{https://doi.org/10.1086/664613}.

@@

\ifen Kim, Minhee. 2015. ``[College application strategy] Six chances total\dots divide applications across reach, target, and safety schools'' (in Korean). Jungang Ilbo, Aug. 26. \url{https://doi.org/10.1086/664613}\fi
